Maximizing Ink in Symmetric Partial Edge Drawings of $k$-plane Graphs

### 2018-01-09 eurocg/paper.tex
minor sec 3 changes

%------------------------------------------------------------------- 
%if unwanted, comment out or use option "draft"
\usepackage{todonotes}
\usepackage{microtype}
\usepackage[noend, linesnumbered]{algorithm2e}
\usepackage{amsmath}
\usepackage{color}
\usepackage{cite}
\usepackage{pifont}
\usepackage{enumerate}
\usepackage[basic]{complexity}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{graphicx}

@@

%\begin{proof}
	We reduce from the \NP-hard problem \ppsat~\cite{l-pftu-82} using similar ideas as in Bruckdorfer's general proof of the hardness of \maxsped~\cite{b-sgh-15}. %, which reduces from the more restricted problem \textsc{Planar Positive 1-in-3 Sat}. 
	Let $\phi$ be a planar 3-Sat formula with $n$ variables $\{x_1, \dots, x_n\}$ and $m$ clauses $\{c_1, \dots, c_m\}$, each consisting of three literals.
	We can assume that $\phi$ comes with a planar drawing of its variable-clause graph $H_\phi$ that has a vertex for each variable $x_i$ placed on a horizontal line and a vertex for each clause $c_j$ either above or below the horizontal line and connected on that side of the line to the three variables appearing in $c_j$. 
	In our gadget-based reduction we mimic the drawing of $H_\phi$ by creating a 3-plane drawing $\Gamma_\phi$ as a set of line segments of uniform length and a value $L$ such that $\Gamma_\phi$ has a SPED with ink at least $L$ if and only if $\phi$ is satisfiable.
	Figure~\ref{fig:gadget_connection} shows a sketch of the gadgets.

		\begin{figure}
%	\begin{wrapfigure}[15]{r}{0.55\textwidth}
			\centering
			\includegraphics{Reduction_visual}
			\caption{Example of three variable gadgets and a satisfied clause gadget. Dotted parts do not belong to the SPED.}
			\label{fig:gadget_connection}
%	\end{wrapfigure}		
		\end{figure}
	All segments in the gadgets are of length 5.
	We use pairs of intersecting segments, alternatingly colored red and green.
	The intersection point of each red-green segment pair is at distance 1 from an endpoint.
	Thus the maximum amount of ink contributed by such a pair is 7 (one full segment of length 5 and the other one with two stubs of length 1 each).

	Each variable gadget is a cycle of segment pairs, with at least one pair for each occurence of the variable in $\phi$, see Fig.~\ref{fig:gadget_connection}. 
	Observe that this cycle has exactly two ink-maximal SPEDs: either all red edges are full segments and all green edges are length-1 stubs or vice versa.
	We associate the configuration with full red segments and green stubs with the value \emph{true} and the configuration with full green segments and red stubs with the value \emph{false}.

@@

	Conversely, assume that we have a SPED with ink value $L$. 
	By construction, every red-green segment pair and every clause gadget must contribute its respective maximum ink value.
	In particular, each variable gadget is either in state \emph{true} or \emph{false}.
	We claim that this truth assignment satisfies $\phi$.
	For each clause, one segment must have full length and as argued before the path connecting that segment to a variable gadget must have all segments at even positions as length-1 stubs and all segments at odd positions as full segments. 
	In particular the first segment of the literal path is fully drawn and therefore in a SPED with ink $L$ the intersecting segment of the variable cannot be fully drawn.
	In fact, it must be drawn as length-1 stubs for otherwise the variable gadget would not contribute its maximum ink value.
	But then by construction the selected variable value sets our literal to \emph{true}.
%\end{proof}

@@

Section~\ref{sec:hardness} showed that \maxsped is generally \NP-hard for $k \ge 3$. 
Now we consider the special case that the intersection graph of the $k$-plane input drawing is a tree or a cactus. In both cases we present polynomial-time dynamic programming algorithms. Let $ C = (V,E) $ be the intersection graph of a given drawing $\Gamma$ of graph $ G $ as defined in Section~\ref{sec:preliminaries}. 
Let $ u \in V $ and $ \deg(u) = \delta $. 
Then for the corresponding segment $ s(u) \in S $ there are $ \delta + 1 $ relevant stub pairs including the whole segment, see Fig.~\ref{fig:tree}. 
Let $ \ell_1(u), \dots, \ell_\delta(u) \in \mathbb{R}_+$ be the stub lengths induced by the intersection points of $s(u)$ with the segments of the neighbors of $u$,  sorted from shorter to longer stubs. We define  $ \ell_0(u) $ as the length of the whole segment $ s(u) $.

@@

	\sollong(u) = \max\{T_0(u),\dots,T_{\delta}(u)\}

@@

\begin{theorem}
	\label{thm:tree}
	Let $ G $ be a simple graph with $m$ edges and $ \Gamma $ a straight-line drawing of $ G $. If the intersection graph $ C = (V,E) $ of $ G $ is a tree with maximum degree $ k \in \mathbb{N} $ problem \maxsped can be solved in $ O(mk + m \log m)) $ time and space.
\end{theorem}
% \begin{proof}
% 	Since $ C $ is known to be a tree, and hence $ |E| = O(m) $, we can compute the intersection graph and the stub lengths in $ O(m\log m) $ time and space.
% 	With Lemma~\ref{lem:compute_vertex} and Recurrence~\ref{rec:tree} we need one pass through the tree to find the roots maximum in $ O(mk) $ time. Adding the bounds yields the desired runtime of $ O(mk + m \log m)) $.
% %	To solve the \maxsped problem on $ G $ we need to compute $ \max \{T_i(r) \mid 0 \leq i \leq k \} $ for the root $ r \in V $ of $ C $ as seen above. Doing this bottom up requires one pass through $ C $ hence by applying Lemma~\ref{lem:compute_vertex} we need $ O(mk) $ time to compute all $ T_i(u) $ for all $ u \in V $. For every vertex we only need to compute $ O(k) $ values and store two of them, namely $ \sollong(u) $ and $ \solshort(u) $, so we do not need more than $ O(mk) $ memory. Adding the bounds yields the desired runtime of $ O(mk + m \log m)) $.
% %
%
%
%
% 	Retrieving the actual stub length for each edge in $ G $ needed to produce the SPED can be done by backtracking the subsolutions which requires at most $ O(mk) $ time.
% \end{proof}

@@

\subsection{Cacti}
\label{sec:cactus}
In this section we restrict $ C = (V,E) $ to be a cactus graph, i.e. a simple graph in which no edge $ e \in E $ is part of more than one cycle. For a cactus graph $ C $ the \emph{block-cut tree} is the tree $ \mathcal T = (\mathcal V, \mathcal E) $ where $ \mathcal V $ contains a vertex for every cycle and cut vertex in $ C $. We call a vertex $ u \in \mathcal V $ a \emph{block vertex} if it represents an induced cycle with vertices $ V_c \subseteq V $ and \emph{articulation vertex} of the cut vertex $ v \in V $ else. For a block vertex $ u \in \mathcal V $ we define $ \textit{cycle}(u) = V_c$ and for an articulation vertex $ u \in \mathcal V $ we define $ A(u) = v $. There is an edge $ uv \in \mathcal E $ between a block vertex $ u $ and articulation vertex $ v $ whenever $ v \in \textit{cycle}(u) $ and an edge $ uv \in \mathcal E $ between two articulation vertices whenever $ A(u)A(v) $ was an edge in $ E $.

Let $ C = (V,E) $ be a cactus graph and moreover the intersection graph of a graph $ G $ and straight-line drawing $ \Gamma $. Additionally let $ \mathcal T = (\mathcal V, \mathcal E) $ be the block-cut tree of $ C $ we define for each vertex $ u \in \mathcal V $ two indices $ i_p,i_q $, w.l.o.g $ i_p > i_q $. This are exactly the indices of the stub-lengths leading to an intersection between two cycles of segments in $ \Gamma $. Similar to Section~\ref{sec:tree} we define three values for every vertex $ u \in \mathcal V $ with degree $ \delta $:
\begin{align*}
	\solshort(u) = \max\{T_0(u),\dots,T_\delta(u)\}\\
	\solmid(u) = \max\{T_1(u),\dots,T_{i_p}(u)\}\\
	\sollong(u) = \max\{T_1(u),\dots,T_{i_q}(u)\}
\end{align*}
For an articulation vertex $ u \in \mathcal V $ we can define a similar recurrence to Recurrence~\ref{rec:tree}:
\begin{align}
\label{rec:cactus_articulation}
T_i(u) = \ell_i(A(u)) + \sum_{v \in c(u)}
\begin{cases}
\solshort(v) & \text{if } \ell_i(A(u)) \leq a \\
\solmid(v) & \text{if } a < \ell_i(A(u)) \leq b \\
\sollong(v) & \text{else}
\end{cases}
\end{align}
For a block vertex $ u \in \mathcal V $ we have to cut open the cycle it represents (compare \cite{bcgkmn-pped-17}). We do this at $ A(p(u)) $. The resulting graph is a path over the vertices in $ \textit{cycle}(u) $ with attached articulation vertices. This is especially a tree and we use the aglorithm from Section~\ref{sec:tree}, maximizing over three values of the articulation vertices though,  to compute the $ T_i(u) $.

The correctness follows as in the case of a tree in Section~\ref{sec:tree} if the values computed for the block vertices is correct. This is the case since we only extended the cycle by attaching some leafs, which can be dealt with after cutting the cycle open as in \cite{bcgkmn-pped-17}. For the runtime we can again do the same as in Section~\ref{sec:tree}, but this time we have to also check cycles of length $ n_c $ which leads to a runtime of $ O(n_c\delta) $ for a block vertex $ u \in \mathcal V $ with degree $ \delta $ and $ n_c = |\textit{cycle}(u)| $. In case $ u $ is an articulation vertex we can solve it in $ O(\delta) $. As before the optimal solution to the \maxsped problem on $ G $ with drawing $ \Gamma $ can be found by backtracking from the root. Additionally the intersection graph can be computed in $ O(m\log m) $ where $ m $ is the number of edges in the original graph $ G $ and we obtain the following theorem.

@@

\begin{theorem}
	Let $ G $ be a simple graph with $m$ edges and $ \Gamma $ a straight-line drawing of $ G $. If the intersection graph $ C = (V,E) $ of $ G $ is a cactus with maximum degree $ k \in \mathbb{N} $ the \maxsped problem can be solved in $ O(mk + m \log m)) $ time and space.
\end{theorem}
%\begin{proof}
%	Follows as in Theorem~\ref{thm:tree} by maximizing over the tree using Recurrence~\ref{rec:cactus_articulation}. Then the running time follows from constructing the intersection graph and the block-cut tree as well as Lemma~\ref{lem:compute_block} for the block vertices and applying Lemma~\ref{lem:compute_vertex} for the articulation vertices.
%\end{proof}

\bibliography{paper}
\end{document}

@@

\begin{figure}
	\centering
	\includegraphics[width=.8\linewidth]{variable_clause_connection}
	\caption{Connection between the clause and variable gadgets, created by chains of an even number of segments.}
	\label{fig:gadget_connection}
\end{figure}

>>>>

%------------------------------------------------------------------- 
%if unwanted, comment out or use option "draft"
\usepackage{todonotes}
\usepackage{microtype}
\usepackage[noend, linesnumbered]{algorithm2e}
\usepackage{amsmath}
\usepackage{color}
\usepackage{cite}
\usepackage{pifont}
\usepackage{enumerate}
\usepackage[basic]{complexity}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{graphicx}
%\usepackage{cutwin}

@@

%\renewcommand\windowpagestuff{%
%	\includegraphics{Reduction_visual}
%	\captionof{figure}{Example of three variable gadgets and\\ a satisfied clause gadget. Dotted parts do not belong\\ to the SPED.}
%	\label{fig:gadget_connection}
%}
%\opencutleft
\begin{proof}
%		\begin{cutout}{2}{0pt}{0.44\textwidth}{15}
	We reduce from the \NP-hard problem \ppsat~\cite{l-pftu-82} using similar ideas as in Bruckdorfer's general proof of the hardness of \maxsped~\cite{b-sgh-15}. %, which reduces from the more restricted problem \textsc{Planar Positive 1-in-3 Sat}. 
	Let $\phi$ be a planar 3-Sat formula with $n$ variables $\{x_1, \dots, x_n\}$ and $m$ clauses $\{c_1, \dots, c_m\}$, each consisting of three literals.
	We can assume that $\phi$ comes with a planar drawing of its variable-clause graph $H_\phi$ that has a vertex for each variable $x_i$ placed on a horizontal line and a vertex for each clause $c_j$ either above or below the horizontal line and connected on that side of the line to the three variables appearing in $c_j$. 
	In our gadget-based reduction we mimic the drawing of $H_\phi$ by creating a 3-plane drawing $\Gamma_\phi$ as a set of line segments of uniform length and a value $L$ such that $\Gamma_\phi$ has a SPED with ink at least $L$ if and only if $\phi$ is satisfiable.
	Figure~\ref{fig:gadget_connection} shows a sketch of the gadgets.
%		\end{cutout}

		\begin{figure}
%	\begin{wrapfigure}[15]{r}{0.55\textwidth}

			\centering
\includegraphics{Reduction_visual}
\caption{Example of three variable gadgets and a satisfied clause gadget. Dotted parts do not belong to the SPED.}
\label{fig:gadget_connection}
%	\end{wrapfigure}		
		\end{figure}
	All segments in the gadgets are of length 5.
	We use pairs of intersecting segments, alternatingly colored red and green.
	The intersection point of each red-green segment pair is at distance 1 from an endpoint.
	Thus the maximum amount of ink contributed by such a pair is 7 (one full segment of length 5 and the other one with two stubs of length 1 each).

	Each variable gadget is a cycle of segment pairs, with at least one pair for each occurence of the variable in $\phi$, see Fig.~\ref{fig:gadget_connection}. 
	Observe that this cycle has exactly two ink-maximal SPEDs: either all red edges are full segments and all green edges are length-1 stubs or vice versa.
	We associate the configuration with green stubs and full red segments with the value \emph{true} and the configuration with full green segments and red stubs with the value \emph{false}.

@@

	Conversely, assume that we have a SPED with ink value $L$. 
	By construction, every red-green segment pair and every clause gadget must contribute its respective maximum ink value.
	In particular, each variable gadget is either in state \emph{true} or \emph{false}.
	We claim that this truth assignment satisfies $\phi$.
	For each clause, one segment must have full length and as argued before the path connecting that segment to a variable gadget must have all segments at even positions as length-1 stubs and all segments at odd positions as full segments. 
	In particular the first segment of the literal path is fully drawn and therefore in a SPED with ink $L$ the intersecting segment of the variable cannot be fully drawn.
	In fact, it must be drawn as length-1 stubs for otherwise the variable gadget would not contribute its maximum ink value.
	But then by construction the selected variable value sets our literal to \emph{true}.	
\end{proof}

@@

Section~\ref{sec:hardness} showed that \maxsped is generally \NP-hard for $k \ge 3$. 
Now we consider the special case that the intersection graph of the $k$-plane input drawing is a tree or a cactus. In both cases we present polynomial-time dynamic programming algorithms. Let $ C = (V,E) $ be the intersection graph of a given drawing $\Gamma$ of graph $ G $ as defined in Section~\ref{sec:preliminaries}. 
Let $ u \in V $ and $ \delta  = \deg(u) $. 
Then for the corresponding segment $ s(u) \in S $ there are $ \delta + 1 $ relevant stub pairs including the whole segment, see Fig.~\ref{fig:tree}. 
Let $ \ell_1(u), \dots, \ell_\delta(u) \in \mathbb{R}_+$ be the stub lengths induced by the intersection points of $s(u)$ with the segments of the neighbors of $u$,  sorted from shorter to longer stubs. We define  $ \ell_0(u) $ as the length of the whole segment $ s(u) $.

@@

	\sollong(u) = \max\{T_0(u),\dots,T_{\delta}(u)\}.

@@

\begin{theorem}
	\label{thm:tree}
	Let $ G $ be a simple graph with $m$ edges and $ \Gamma $ a straight-line drawing of $ G $. If the intersection graph $ C = (V,E) $ of $ G $ is a tree with maximum degree $ k \in \mathbb{N} $ problem \maxsped can be solved in $ O(mk + m \log m) $ time and space.
\end{theorem}
% \begin{proof}
% 	Since $ C $ is known to be a tree, and hence $ |E| = O(m) $, we can compute the intersection graph and the stub lengths in $ O(m\log m) $ time and space.
% 	With Lemma~\ref{lem:compute_vertex} and Recurrence~\ref{rec:tree} we need one pass through the tree to find the roots maximum in $ O(mk) $ time. Adding the bounds yields the desired runtime of $ O(mk + m \log m)) $.
% %	To solve the \maxsped problem on $ G $ we need to compute $ \max \{T_i(r) \mid 0 \leq i \leq k \} $ for the root $ r \in V $ of $ C $ as seen above. Doing this bottom up requires one pass through $ C $ hence by applying Lemma~\ref{lem:compute_vertex} we need $ O(mk) $ time to compute all $ T_i(u) $ for all $ u \in V $. For every vertex we only need to compute $ O(k) $ values and store two of them, namely $ \sollong(u) $ and $ \solshort(u) $, so we do not need more than $ O(mk) $ memory. Adding the bounds yields the desired runtime of $ O(mk + m \log m)) $.
% %
%
%
%
% 	Retrieving the actual stub length for each edge in $ G $ needed to produce the SPED can be done by backtracking the subsolutions which requires at most $ O(mk) $ time.
% \end{proof}

@@

\subsection{Cacti}
\label{sec:cactus}
In this section we restrict $ C = (V,E) $ to be a cactus graph, i.e. a simple graph in which no edge $ e \in E $ is part of more than one cycle. For a cactus graph $ C $ the \emph{block-cut tree} is the tree $ \mathcal T = (\mathcal V, \mathcal E) $ where $ \mathcal V $ contains a vertex for every cycle and cut vertex in $ C $. We call a vertex $ u \in \mathcal V $ a \emph{block vertex} if it represents an induced cycle with vertices $ V_c \subseteq V $ and \emph{articulation vertex} representing the cut vertex $ v \in V $ else. For a block vertex $ u \in \mathcal V $ we define $ \textit{cycle}(u) = V_c$ and for an articulation vertex $ u \in \mathcal V $ we define $ A(u) = v $. There is an edge $ uv \in \mathcal E $ between a block vertex $ u $ and articulation vertex $ v $ whenever $ v \in \textit{cycle}(u) $ and an edge $ uv \in \mathcal E $ between two articulation vertices whenever $ A(u)A(v) $ was an edge in $ E $.

Let $ C = (V,E) $ be a cactus graph and moreover the intersection graph of a graph $ G $ with straight-line drawing $ \Gamma $. Additionally let $ \mathcal T = (\mathcal V, \mathcal E) $ be the block-cut tree of $ C $ we define for each vertex $ u \in \mathcal V $ two indices $ i_p,i_q $, w.l.o.g $ i_p > i_q $. This are exactly the indices of the stub-lengths leading to an intersection between two cycles of segments in $ \Gamma $. Similar to Section~\ref{sec:tree} we define three values for every vertex $ u \in \mathcal V $ with degree $ \delta $:
\begin{align*}
	\solshort(u) &= \max\{T_0(u),\dots,T_\delta(u)\}\\
	\solmid(u) &= \max\{T_1(u),\dots,T_{i_p}(u)\}\\
	\sollong(u) &= \max\{T_1(u),\dots,T_{i_q}(u)\}
\end{align*}
%\begin{eqnarray*}
%	\solshort(u) = \max\{T_0(u),\dots,T_\delta(u)\}\qquad
%	\solmid(u) = \max\{T_1(u),\dots,T_{i_p}(u)\}\\
%	\multicolumn{2}{c}{$\sollong(u) = \max\{T_1(u),\dots,T_{i_q}(u)\}$}
%\end{eqnarray*}
For an articulation vertex $ u \in \mathcal V $ we can define a similar recurrence to Recurrence~\ref{rec:tree}:
\begin{align}
\label{rec:cactus_articulation}
T_i(u) = \ell_i(A(u)) + \sum_{v \in c(u)}
\begin{cases}
\solshort(v) & \text{if } \ell_i(A(u)) \leq a \\
\solmid(v) & \text{if } a < \ell_i(A(u)) \leq b \\
\sollong(v) & \text{else}
\end{cases}.
\end{align}
For a block vertex $ u \in \mathcal V $ we have to cut open the cycle it represents (compare \cite{bcgkmn-pped-17}). We do this at $ A(p(u)) $. The resulting graph is a path between the vertices in $ \textit{cycle}(u) $ with attached articulation vertices. This is especially a tree and we use the aglorithm from Section~\ref{sec:tree}, maximizing over three values of the articulation vertices though,  to compute the $ T_i(u) $.

If the values computed for the block vertices is correct, we can follow the correctness of the algorithm as in Section~\ref{sec:tree}. Let $ u \in \mathcal V $ be a block vertex then by \cite{bcgkmn-pped-17} we know the optimal solution for \maxsped just on $ C[\textit{cycle}(u)] $ is correctly computed by the above procedure since the algorithm from Section~\ref{sec:tree} correctly handles the created path. Now if $ u $ has articulation vertices attached to it the above computes the correct value since this is simply a tree. Further there is no $ v \in c(u) $ which is not an articulation vertex, hence the maximum ink value for $ u $ is correctly computed if we know the values for the children in $ c(u) $.

For the runtime we can again argue the same as in Section~\ref{sec:tree}, but this time we have to also check cycles of length $ n_c $ which leads to a runtime of $ O(n_ck^2) $ for a block vertex $ u \in \mathcal V $ with $ n_c = |\textit{cycle}(u)| $. In case $ u $ is an articulation vertex we can solve it in $ O(k) $. As before the optimal solution to the \maxsped problem on $ G $ with drawing $ \Gamma $ can be found by backtracking from the root. Additionally the intersection graph can be computed in $ O(m\log m) $ where $ m $ is the number of edges in the original graph $ G $ since $ |E| = O(m) $ in a cactus and we obtain the following theorem.

@@

\begin{theorem}
	Let $ G $ be a simple graph with $m$ edges and $ \Gamma $ a straight-line drawing of $ G $. If the intersection graph $ C = (V,E) $ of $ G $ is a cactus with maximum degree $ k \in \mathbb{N} $ the \maxsped problem can be solved in $ O(mk^2 + m \log m) $ time and space.
\end{theorem}
%\begin{proof}
%	Follows as in Theorem~\ref{thm:tree} by maximizing over the tree using Recurrence~\ref{rec:cactus_articulation}. Then the running time follows from constructing the intersection graph and the block-cut tree as well as Lemma~\ref{lem:compute_block} for the block vertices and applying Lemma~\ref{lem:compute_vertex} for the articulation vertices.
%\end{proof}

%\bibliography{paper}
\begin{thebibliography}{1}

	\bibitem{bew-vnd-95}
	Richard~A. Becker, Stephen~G. Eick, and Allan~R. Wilks.
	\newblock Visualizing network data.
	\newblock {\em {IEEE} Trans. Visualization and Computer Graphics}, 1(1):16--28,
	1995.

	\bibitem{blmt-pedhmitc-16}
	Carla Binucci, Giuseppe Liotta, Fabrizio Montecchiani, and Alessandra Tappini.
	\newblock Partial edge drawing: Homogeneity is more important than crossings
	and ink.
	\newblock In {\em Information, Intelligence, Systems Applications (IISA'16)},
	pages 1--6. IEEE, 2016.

	\bibitem{b-sgh-15}
	Till Bruckdorfer.
	\newblock {\em Schematics of Graphs and Hypergraphs}.
	\newblock PhD thesis, Uni Tübingen, 2015.

	\bibitem{bcgkmn-pped-17}
	Till Bruckdorfer, Sabine Cornelsen, Carsten Gutwenger, Michael Kaufmann,
	Fabrizio Montecchiani, Martin Nöllenburg, and Alexander Wolff.
	\newblock Progress on partial edge drawings.
	\newblock {\em J. Graph Algorithms Appl.}, 21(4):757--786, 2017.

	\bibitem{bk-ecbe-12}
	Till Bruckdorfer and Michael Kaufmann.
	\newblock Mad at edge crossings? {Break} the edges!
	\newblock In {\em Fun with Algorithms (FUN'12)}, volume 7288 of {\em LNCS},
	pages 40--50. Springer, 2012.

	\bibitem{bkl-us-15}
	Till Bruckdorfer, Michael Kaufmann, and Simon Leibßle.
	\newblock Ped user study.
	\newblock In {\em Graph Drawing (GD'15)}, volume 9411 of {\em LNCS}, pages
	551--553. Springer International Publishing, 2015.

	\bibitem{bvkw-epdldge-12}
	Michael Burch, Corinna Vehlow, Natalia Konevtsova, and Daniel Weiskopf.
	\newblock Evaluating partially drawn links for directed graph edges.
	\newblock In {\em Graph Drawing (GD'11)}, volume 7034 of {\em LNCS}, pages
	226--237. Springer, 2012.

	\bibitem{bcko-cgaa-08}
	Mark de~Berg, Otfried Cheong, Marc van Kreveld, and Mark Overmars.
	\newblock {\em Computational Geometry: Algorithms and Applications}.
	\newblock Springer, 3rd edition edition, 2008.

	\bibitem{l-pftu-82}
	David Lichtenstein.
	\newblock Planar formulae and their uses.
	\newblock {\em SIAM J Comput}, 11(2):329--343, 1982.	
\end{thebibliography}
\end{document}

@@

\begin{figure}
	\centering
	\includegraphics[width=.8\linewidth]{variable_clause_connection}
	\caption{Connection between the clause and variable gadgets, created by chains of an even number of segments.}
%	\label{fig:gadget_connection}
\end{figure}
